# Daily journal

## 2021-10-07

Working on *collaborative workflow* for FIMS I found this
[training](https://codebender.org/) for workflows on GitHub.
They advocate for Git Flow in all workflows.

## 2021-10-06

Trevor Riley of the NOAA library and I talked about 508 compliance and NOAA citations.
Typically, when a NOAA librarian helps you with a document they recommend
Cite While You Write combined with EndNote.
The NOAA library is working on getting a single, integrated Endnote library but
this is not currently available.
Instead, they have Endnote libraries from individual projects.

### Institutional Repository

All NOAA funded and NOAA published documents are supposed to be entered into the
[Institutional Repository](repository.library.noaa.gov)
The goal is to get all entries starting from 2015 to current year.
They will accept entries from any year though.

The Institutional Repository uses NOAA resources to check metadata and assign a DOI.
Assigning a DOI to all stock assessment documents would facilitate cataloging them.
RIS file could be batch downloaded and converted to a bib file.

Everything in the repository should be 508 compliant and
is checked internally using [a standard](https://libguides.library.noaa.gov/Section508).
Jamie works on compliance issues every day and
Jennifer has a good handle on it.
Their guidance is summarized in the 
[Quick Start](https://libguides.library.noaa.gov/Section508/QuickStart) Big 5 list.

- [x] send .bib file to Trevor
- [x] look at the link that Trevor sent to find how many assessments are
  actually in the institutional repository

### EndNote library

* 200 projects
* 60 species and projects outside of species research
* all archived libraries from different projects
* goal is to bring it into a single repository that could be shared
* starting with Endangered Species Act work
* do not manually check information from a publisher or tell publishers when information is incorrect

#### Import of bib file to EndNote

Trevor tried importing the Lingcod.bib file from the 2021 assessment and no metadata was found.
I did a quick google search and found that Imperial College London has
[advice on LaTeX with EndNote](https://www.imperial.ac.uk/media/imperial-college/administration-and-support-services/library/public/LaTeX-and-Endnote-apr-2019.pdf)
with
[filters](https://www.imperial.ac.uk/admin-services/library/learning-support/reference-management/endnote/)
that are needed to import .bib entries.
Even with these filters, the ability of EndNote to recognize metadata is not great.

## 2021-09-17

### [Z{\"o}ller et al. 2020](https://doi.org/10.1016/j.techfore.2020.120291)

As the workforce turns more towards remote work,
decisions are becoming more local (Capra and Luisi, 2016).
FLOSS-based groups are becoming more like a bazaar,
structured horizontally and maintained by modular self-organized teams without central management,
rather than a cathedral, e.g.,
Linux and Fetchmail.
Schrape (2018) suggest that with corporate influence in FLOSS there are four types of open source projects,

  1. Corporate-led collaboration projects characterized by clear hierarchies,
  2. Hierarchical infrastructure projects that are largely run by nonprofits with horizontal structures,
  3. Elite-centered project communities that are hierarchical centered around a few core developers, and
  4. Egalitarian oriented peer production communities that maintain horizontal structure.

The 'onion' model suggests that newcomers move through the ranks by

  1. Contributing to bug fixes, documentation, small feature improvements, and discussion;
  2. Eventually becoming a core developer and contributing to pull requests.

Pull requests dictate the groups hierarchy.
Small groups (3-7) are the primary settings for socialization, skill transfer, and the delegation of duties (Snow et al., 1986).
Medium-sized groups (8-20) allow complex interdependent coordination.
Decentralized groups perform better on complex tasks than centralized groups.
More centralized communication patterns developed in groups that performed simple discrete tasks.

**Goal settings and quality control** are important group functions that require establishing a decision process.
Resilient projects have complex structure with more than one person accepting pull requests.
These complex groups maintained contributors and were more productive than star-shaped groups with a single person designated to accept pull requests.

Sharing information publicly reduces the burden of coordination creating less logistical overhead.

## 2021-08-16

### Thesis Chapter 1

https://besjournals.onlinelibrary.wiley.com/doi/epdf/10.1111/2041-210X.12188
https://academic.oup.com/icesjms/article/77/7-8/2529/5912155#223391660
https://www.semanticscholar.org/paper/Estimation-and-classification-of-temporal-trends-to-Solvang-Planque/5f5727f6f2b3512ee5d9dc2e1258a7c75ed02ded
https://www.semanticscholar.org/paper/A-simulation-study-of-trend-detection-methods-for-Hardison-Perretti/c679d003c94b70d587fa9be62f8a11911dc7944b#citing-papers
https://github.com/nwfsc-timeseries/tvvarss::simTVVAR.R
https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/arima.sim
https://github.com/seanhardison1/soe_simulations/blob/master/R/sim_function.R
https://github.com/kellijohnson-NOAA/tsrelation/blob/master/R/tvvarss_simTVVAR.R
https://github.com/fate-ewi/bayesdfa::sim.R
https://journal.r-project.org/archive/2019/RJ-2019-007/index.html

### Hake recruitment

https://github.com/seanhardison1/soe_simulations/blob/master/R/sim_function.R

## 2021-06-10

### Rstudio community talk - [Building Effective Data Science Teams](https://www.rstudio.com/resources/webinars/building-effective-data-science-teams/)

#### Prioritization

You will only ever have time to do 10\% of the work.
Therefore, it is important to have a list of tasks that are clearly defined and
when a new task comes in it must be prioritized against the current list.
Looking at a new task relative to the current list is important because
if you want to work on the newly added task, then something else will
need to be moved down the list.

## 2021-06-03

### utils::file_test

Check if a file is a directory or file and if it exists or not.
You can also test if a file is newer than or older than another file.

I found this function while perusing the
[bookdown::render_book](https://github.com/rstudio/bookdown/blob/master/R/render.R) function.
It is used inside of an if statement, where the check is saved to an object,
something I did not know how to do. I always thought you had to save it outside
and then test it. For example,
```{r utils-file_test, eval = FALSE}
  if (!all(exist <- file_test("-f", input))) {
    stop("Some files were not found: ",  paste(input[!exist], collapse = ' '))
  }
```

### Openscapes

The openscapes training that Eric Ward set up helped to validate my workflow,
which has been a great productivity generator for me because it often seemed like
I was wasting time organizing and using such rigid standards.
It is NOT a waste of time. Helping my future self not hate my job is legitimate.

Yesterday, I got feedback from PEP on my talk about sa4ss for the L-team.
The previous day I got feedback from KM on the same talk.
Both experiences were helpful.
I learned that the more organized you are and
the better the story of your first and last slides are,
the better the information will be received.

### R `desc`

The `desc` package helps to read, parse, and edit DESCRIPTION files.

`desc::desc_get_dps(file = "")` provides a list of all dependencies in the
DESCRIPTION file for a given package passed to file.

### Pacific hake otolith exchange

Exchange of 100 otoliths with DFO

#### Timing

Exchange fish from a single year.

Fish from early in the year are harder to age because the annulus isn't as defined.
Age readers often do fine when they know when the fish was landed because
they can correct their read for the timing.

Survey ages will be coming to the lab later this year because of covid
protocols that delay the timing of things.

#### Bottom trawl survey are harder to read

The ages from the bottom trawl survey for hake are hard to read.
They are patchy and faint. Not recommended for a beginning reader.

- genetic testing of hake fin clips from the two different surveys,
midwater versus bottom trawl.

#### Alternative methods for younger fish

Fish length, **otolith weight**, spectroscopy, ...

Large year classes are hard to age when there are lots of little fish.

- [ ] Plot length distribution of age reads across years to see how consistent they are.

## 2021-05-29

### Confidence intervals

When working with R, you can find the confidence interval of an estimate that
is assumed to have a normal distribution using the stats package.

```{r r-confidenceintervals-crit, echo = TRUE}
crit <- stats::qnorm(
  p = 1 - (1 - 0.95) / 2,
  mean = 0,
  sd = 1,
  lower.tail = TRUE,
  log.p = FALSE
)
print(crit)
```

will find the z score that is associated with a 95\% confidence interval.
One can change the value of 0.95 to any value between zero and one.
This z-score is then multiplied by the standard error and both
subtracted and added to the estimate to give a confidence interval.
You can also multiply it by the standard deviation, but for small sample sizes
the standard deviation needs to be corrected for sample size.

### keywords

confidence interval
statistics

## 2021-05-27

### Lingcod CARE

*   Mark Terwilliger (California): they do not age their own lingcod fins but they do
    process them
      * WDFW ages commercial samples, just under 1200 fins
      * Laurel Lam aged sport samples, 260 samples per year,
      * Mark Terwilliger is also currently ageing more sport fishery samples
        as we speak, he taught himself from looking at Laurel's;
        also doing a second read on some structures that Laurel read
      * black rockfish at the SWFSC is their bread and butter and there is no way
        that the SWFSC could age both lingcod and black rockfish at the same time
      * Josie Thompson started looking into using otoliths in
        2009 and 2010 (n = 100)
        to do double reads but nothing came of the study
*   Nikki Paige (Newport)
      * 2008 and back 100 percent aged, since then 2009 only half are aged
      * 300 paired otolith samples, 2016 and 2017 survey data,
        they will be scanned as well as aged via break and burn,
      * 2020 was 2000 fins
      * doesn't use the metal mesh binder clips, instead they use foam mats and pins
*   Andrew Claiborne (WDFW)
      * started production ageing in 2000
      * port-samples do the fin-ray prep
      * considered otoliths 3-4 years ago (n = 119), surface age on otolith
        because the otoliths get noisy as you go south, underageing relative to fin rays
        for the older fish, 5 year old fins appear as 10 year old otolith fish,
        older fish were fine, another couple hundred of pairs are available;
        like sablefish, if you only look at break and burn reads will be off but
        surface reads will help guide break and burn reads;
*   Stephen Wischniowski
      * 400-450 per year, 2021 == 1500 b/c they are behind, only age fin rays
      * currently sampling oldest and youngest fish to do a comparison study
*   Kevin McNeel (SE Alaska)
      * fishers only return sampled fish
      * getting sex data along with otolith data is important
*   Chris Hinds (ADF&G ADU)
      * use otoliths
      * must use nail laqeur b/c they cannot get toxic material b/c there are no roads

## 2021-05-26

### Steering committee

Mix of federal and external participants.

### Cole Monnahan

Regarding how prioritizing is going to happen?
Should we have a spreadsheet with each stock and their requirements.
Rick responded with there is a start to that in SIS because it records basic information
such as what model it is using.
Christine responded with [Stock SMART][stocksmart] or peer-reviewed manuscripts could be helpful.
Stock Smart has information on any stock that has an FMP.

As of 2019, 50 assessments are in SIS are VPA and 62 are SCAA
according to StockSMART.

[stocksmart]: https://www.st.nmfs.noaa.gov/stocksmart?app=homepage

## 2021-05-26

### Rethink Reporting with Automation by Claudio Rebelo and RStudio presentation

#### Abstract

Companies struggle with reporting.
Specifically, they’re caught in a cycle of inefficient and error-prone workflows that:

*   Place a burden on individual data scientists when reports need to be repeated, updated, or shared.
*   Prevent decision-makers and business users from getting important, accurate insights in a timely manner.

Resulting in enormous amounts of resources (people, tools, time)
are invested into delivering a mediocre product to stakeholders,
reports that are uninspiring to consume, slow to produce, and potentially not accurate.

On May 26th, we invite you to join
Claudio Rebelo, Actuary at Swiss Re,
to learn about how companies in every industry, but especially in insurance,
can revolutionize their reporting capabilities with automation.

You’ll learn about his team’s journey transitioning from a reporting frankenstack,
involving SAS, Excel, and SQL, to a more effective way with free, open-source tools like R Markdown.

The goal is to inspire you to think about
what could be possible when it comes to reporting within your own organization,
with just a little bit of effort.
You’ll get a high-level overview of Claudio and Swiss Re’s journey,
along with concrete tactical tips on how to use tools like R Markdown more effectively.

If you’re a team-lead or business user without much experience with R, you’ll learn:

*   The consequences associated with traditional, messy reporting workflows.
*   The benefits of automation when it comes to reporting.
*   How to incorporate open-source tools like R Markdown into a corporate environment.

If you’re a data scientists already experienced with R and R Markdown you’ll learn:

*   How to enhance your reporting with Shiny and parameterized reports.
*   How to automate QA and collaboration tasks, like commenting.
*   About new packages for specific tasks.

If you’re a data scientists already experienced with R, but not automating reports with tools like R Markdown

We hope this presentation inspires you to start ASAP!

#### About the speaker

Claudio Rebelo / Actuary at Swiss Re
Claudio Rebelo is an Actuary at Swiss Re in Zurich, Switzerland,
where he has worked in reserving, pricing and currently model validation,
having over 12 years of experience in the insurance industry.
With a keen interest in insurance data visualization he is also involved, at Swiss Re,
in the implementation of automated reporting solutions with R Markdown.

#### R packages

*   DT: searchable tables
*   glue
*   kable
*   plotly
*   officer

#### Bookdown

* Can create word documents.
* Sentence structure
* Create sentences using ifelse statements
  * Paramaterized reports
  *  Use the yaml header with param:
* Special characters can be escaped.
* Spell checker: word provides a lot of options,
but so does RStudio. you can even load your own dictionary.

## Acronyms

* FLOSS - Free/Libre Open Source Software
