# rmarkdown

## Labels

### Section header labels

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro).
If you do not manually label them, there will be automatic labels anyway, e.g.,
where spaces in the section name are translated to dashes.

### Figures and tables

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r figure-create, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(rnorm(5), type = "b", pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g.,
see Figure \@ref(fig:figure-create).
Similarly, you can reference tables generated from `knitr::kable()`, e.g.,
see Table \@ref(tab:table-kable).

```{r table-kable, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

## Citations

Citations can be written using the at symbol.
For example, we are using the **bookdown** package [@R-bookdown] in this sample book,
which was built on top of R Markdown and **knitr** [@xie2015].

### .bib files

You can automatically generate a .bib file for R packages using the following code:

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

## Math

Math can be added in body using usual syntax like this 

$p$ is unknown but expected to be around 1/3. Standard error will be approximated

$$
SE = \sqrt(\frac{p(1-p)}{n}) \approx \sqrt{\frac{1/3 (1 - 1/3)} {300}} = 0.027
$$

You can also use math in footnotes like this^[where we mention $p = \frac{a}{b}$].

We will approximate standard error to 0.027[^longnote]

[^longnote]: $p$ is unknown but expected to be around 1/3. Standard error will be approximated

    $$
    SE = \sqrt(\frac{p(1-p)}{n}) \approx \sqrt{\frac{1/3 (1 - 1/3)} {300}} = 0.027
    $$

## Links

  * [Guide to markdown](https://coderrocketfuel.com/article/a-complete-guide-to-markdown)
